\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\hypersetup{colorlinks=true,urlcolor=blue}
\begin{document}
\begin{center}\huge \bf Installation
\end{center}

\section{Basics}

\indent \indent Start you should be aware that the game engine currently works on Mac and Windows. Each OS has a different method of installation. There will be a different section for each OS that we currently support.

\section{Windows}

\indent \indent  For windows our programmer has made the installation process very easy. All you need to do is download our Release \href{https://github.com/supreme-committee/text-adventure/releases}{Here}. Download the newest version of the Release. Run 'Fork in the Read.exe' to start the game.

\section{Mac}
\subsection{Dependencies:}
    \indent \indent SFML 2.1 (The gcc version) can be downloaded
    \href{http://www.sfml-dev.org/download/sfml/2.1/}{Here}. Simply follow the installation instructions. \\
    \indent Verify that you have the utilities \texttt{tar} and \texttt{make} installed. 
    They should be installed by default. \\
    \indent \texttt{g++} is required. You will need a version of \texttt{g++} which has \texttt{C++11} support.
    We recommend at least \texttt{GCC 4.9}.
    Use \texttt{sudo port install gcc} in order to download and install the 
    latest version of \texttt{gcc}. \\
    \indent A little explanation of the \texttt{Makefile} is warranted. 
    In order to link against the SFML libraries.
    We use the \texttt{-framework} option in \texttt{gcc}. Note that this option is a Mac OSX only option.
    We link against the following modules: 
    \texttt{OpenGL, SFML, SFML-graphics, SFML-window, SFML-system, SFML-audio}.
    Another technology that we use is called RapidXML. We have included the files for RapidXML as it 
    is a header-only implementation.
    
    
\subsection{Installation procedure:}
    \indent \indent To compile from source, \texttt{cd} in to the downloaded directory and type \texttt{make}.
    This will create an executable called \texttt{game}.
    
\end{document}